\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Last night revisions. Fixes #127, fixes #107, fixes #108, fixes #109, fixes #110.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf \usepackage[pdftex]{graphicx} \usepackage{wrapfig} % declare the
% path(s) where your graphic files are
\graphicspath{{pic/}} % and their extensions so you won't have to specify these
% with
% every instance of \includegraphics
\DeclareGraphicsExtensions{.png} \else % or other class option (dvipsone,
% dvipdf, if not using dvips). graphicx
% will default to the driver specified in the system graphics.cfg if no
% driver is specified.
% \usepackage[dvips]{graphicx}
% declare the path(s) where your graphic files are
% \graphicspath{{../eps/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
% \DeclareGraphicsExtensions{.eps}
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{textcomp} \newcommand{\toolname}{Perquimans?!} \begin{document}
	\title{\toolname: A Tool for Visualizing Patterns of Spreadsheet Function Combinations}

	% author names and affiliations
	% use a multiple column layout for up to three different
	% affiliations
	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
		\IEEEauthorblockA{North Carolina State University\\ Raleigh, North Carolina,
			USA} }

@@

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract} Spreadsheet environments often come equipped with an abundance
		of functions and operations to manipulate data, but it can be difficult to
		understand how programmers actually use these functions in practice.
		Furthermore, users can combine several functions into a complex formula,
		complicating matters for both researchers and practitioners who want to study
		formulae to improve spreadsheet practices. Therefore, we developed \toolname, a
		tool that visualizes patterns of function combination in spreadsheets as an
		interactive tree of possibilities, capable of capturing both the most common
		and most anomalous patterns of function combination and their contexts in
		actual workbooks. Using spreadsheets from the Enron corpus, we conduct both a
		case study and several user studies to explore \toolname's various
		applications, particularly those in flexible smell detection and spreadsheet
		education. \end{abstract}

>>>>

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf \usepackage[pdftex]{graphicx} \usepackage{wrapfig} % declare the
\graphicspath{{pic/}} % and their extensions so you won't have to specify these
\DeclareGraphicsExtensions{.png} \else % or other class option (dvipsone,
% dvipdf, if not using dvips). graphicx
% will default to the driver specified in the system graphics.cfg if no
% driver is specified.
% \usepackage[dvips]{graphicx}
% declare the path(s) where your graphic files are
% \graphicspath{{../eps/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
% \DeclareGraphicsExtensions{.eps}
\fi

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{textcomp}

\newcommand{\toolname}{Perquimans }
\newcommand{\toolnameend}{Perquimans}
\newcommand{\toolnameposs}{Perquimans' }

\begin{document}
	\title{\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations}

	% author names and affiliations
	% use a multiple column layout for up to three different
	% affiliations
	\author{ \IEEEauthorblockN{Justin A. Middleton, Emerson Murphy-Hill}
		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ 
			\{jamiddl2, ermurph3\}@ncsu.edu }}

@@

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract} 
		Spreadsheet environments often come equipped with an abundance of functions
		and operations to manipulate data, which users can combine into a complex
		formulae for more sophisticated programs. However, anticipating these
		combinations is difficult, complicating matters for both researchers and
		practitioners who want to study formulae to improve spreadsheet practices.
		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora to
		visualize patterns of function
		combination as an interactive tree, capable
		of representing both the most common and most anomalous patterns of formula construction and their contexts in actual workbooks. Using spreadsheets from
		the Enron corpus, we conduct both a case study and a user study to
		explore \toolnameposs various applications, particularly those in flexible smell
		detection and spreadsheet education.

	\end{abstract}
